The shape of dark matter halos in the AURIGA simulations

### 2019-03-05 Paper/paper.tex
edit

\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
Weak constraint on prolate halo. SDSS stars dynamics.\\\hline

\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
Mid-axis orientation on the outside. \\\hline

\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
stream\\\hline

\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
stream\\\hline

\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
$20$kpc-$60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline

@@

\begin{table*}
\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
Reference&$q_{\rho}$&$s_{\rho}$&$R$&$\theta$&
Methodology\\ 
\hline \hline \citet{Olling_and_Merrifield_2000}& $1.00$
& $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
density. \\\hline

\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&${1}$&${1}$&$9$kpc&$0^{\circ}$&Method:
HI
gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
change between radial regimes.\\\hline

\citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline

\cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline

\citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
20$kpc&$90^{\circ}$ & Stellar streams\\\hline

\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&
$20$kpc-$60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline

@@

\begin{table*}
\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$& Methodology
\\ \hline \hline
\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline

\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&&&$R_{200}$&
For different cosmologies and feedback recipies. Calculated from a fit
at $M_\odot=10^12$\\\hline

>>>>

\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
Weak constraint on prolate halo. SDSS stars dynamics.\\

\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
Mid-axis orientation on the outside. \\

\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
stream\\

\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
stream\\

\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
$20$kpc-$60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline \hline

\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
& Illustris\\

\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
For different cosmologies and feedback recipies. Calculated from a fit
at $M_\odot=10^12$\\\hline

@@

\begin{table*}
\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
Reference&$q_{\rho}$&$s_{\rho}$&$R$&$\theta$&
Methodology\\ 
\hline \hline \citet{Olling_and_Merrifield_2000}& $1.00$
& $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
density. \\

\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&${1}$&${1}$&$9$kpc&$0^{\circ}$&Method:
HI
gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
change between radial regimes.\\

\citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
20$kpc &$0^{\circ}$&Method: SDSS statistics\\

\cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
60$kpc&$0^{\circ}$&Method: Sagittarius stream\\

\citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
20$kpc&$90^{\circ}$ & Stellar streams\\

\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&
$20$kpc-$60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline\hline

@@

\begin{table*}
\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$& Methodology
\\ \hline \hline
